Recurrent Neural Networks

### 2017-12-10 paper/paper.tex
small changes

	Our baseline model is similar to the one proposed in the guided laboratory: input window size of 6 steps, 1 output, 512 LSTM units in one single hidden layer and no dropout.

	Table \ref{t:baseline} shows the results obtained with this model, while figure \ref{f:baseline} shows the evolution of the training and validation loss.

>>>>

	Our baseline model is similar to the one proposed in the guided laboratory: input window size of 6 steps, 1 output, 512 LSTM units in one single hidden layer and no dropout, trained with RMSprop---with a learning rate of 0.0001, $ \rho = 0.9 $, $ \varepsilon = 1 \cdot 10^{-8} $ and no learning rate decay.

	Table \ref{t:baseline} shows the results obtained with this model.
